---
title: "CMSY_GulfGrouper_Free"
author: "Juliette"
date: "October 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages 

```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(sf)
  library(rfishbase)
  library(plotly)
  library(fishmethods)
  library(devtools)
 devtools::install_github("cfree14/datalimited2") 
  library(datalimited2) # Chris Free updated package for CMSY2
})


```


#Load catch data of species
#Loading datset of 7 species with catch data and catch inflated to 20%, 40% and 60% unreported catch 

MT - regular yearly catch 
MT_20 - inflated to 20% unreported catch
MT_40- inflated to 40% unreported catch
MT_60 - inflated to 60% unreported catch
```{r}

#loading catch data of 6 species with more than 5 years of catch data, detailed code for this dataset is in the "landing sites.rmd" in docs 

focalspeciescatch<-read.csv(here("docs", "focalspeciescatch.csv"))

unique(focalspeciescatch$NombreCientifico) #6 species 

#create new data framw with your species of interest
gulf_grouper<-focalspeciescatch%>%
  filter(NombreCientifico=="Mycteroperca jordani")


#Create vectors for the cmsy2 function
year_gulf_grouper <- c(gulf_grouper$Ano) #vector of years
catch_gulf_grouper <- c(gulf_grouper$MT) #vector of catch date 

#new datafram to isolate catch increase by 20%
catch20_gulf_grouper<- c(gulf_grouper$MT_20)
#new datafram to isolate catch increase by 40%
catch40_gulf_grouper<- c(gulf_grouper$MT_40)
#new datafram to isolate catch increase by 60%
catch60_gulf_grouper<- c(gulf_grouper$MT_60)

```


```{r}
#Plots catch over given years, simply change the name of the dataframe ie "Octopus"
graph_GulfGrouper <-ggplot(gulf_grouper, aes(x=Ano, y=MT))+
  geom_line(size=1)+
  ggtitle("Gulf Grouper Catch")+
  geom_point()+
  geom_line()+
  labs(x="Year", y="Yearly total catch catch (MT)")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

ggplotly(graph_GulfGrouper)

```



FAO considers a maximally sustainable fished stock to be between 0.8 and 1.2 BMSY, an overfished stock to be <0.8 BMSY, and an underfished stock to be >1.2 BMSY. For US federally managed fisheries, NOAA reports on what fraction of stocks are overfished (https://www.fisheries.noaa.gov/feature-story/status-stocks-2017), usually defined as being <0.5 BMSY, though the exact ratio differs by region and type of stock

Paper: https://academic.oup.com/icesjms/advance-article/doi/10.1093/icesjms/fsy138/5133277

```{r}

#reslience = very low (from fishbase)

?cmsy2

#Regular landings 
gulf_grouper_cmsy_free <- cmsy2(year=year_gulf_grouper, catch=catch_gulf_grouper, resilience = "Very low")

gulf_grouper_cmsy_free_plots <- plot_dlm(gulf_grouper_cmsy_free)

gulf_grouper_cmsy_free$ref_pts
gulf_grouper_cmsy_free$ref_ts

##results: viable r-k pairs graph is super weird; MSY= 14.149; BMSY < 0.8 = overfished except for 2014 and 2015 which is barely over. BMSY=0.463

#Landings inflated 20%
gulf_grouper_20_cmsy_free <- cmsy2(year=year_gulf_grouper, catch=catch20_gulf_grouper, resilience = "Very low")

gulf_grouper_20_cmsy_free_plots <- plot_dlm(gulf_grouper_20_cmsy_free)

gulf_grouper_20_cmsy_free$ref_pts
gulf_grouper_20_cmsy_free$ref_ts

##results: viable r-k pairs graph is super weird; MSY= 16.945; BMSY < 0.8 = overfished except for 2014 and 2015 which is barely over



#Landings inflated 40%
gulf_grouper_40_cmsy_free <- cmsy2(year=year_gulf_grouper, catch=catch40_gulf_grouper, resilience = "Very low")

gulf_grouper_40_cmsy_free_plots <- plot_dlm(gulf_grouper_40_cmsy_free)

gulf_grouper_40_cmsy_free$ref_pts
gulf_grouper_40_cmsy_free$ref_ts

##results: viable r-k pairs graph is super weird; MSY= 19.908; BMSY < 0.8 = overfished except for 2014 and 2015 which is barely over. 2013 is exactly 8. 


#Landings inflated 60%
gulf_grouper_60_cmsy_free <- cmsy2(year=year_gulf_grouper, catch=catch60_gulf_grouper, resilience = "Very low")

gulf_grouper_60_cmsy_free_plots <- plot_dlm(gulf_grouper_60_cmsy_free)

gulf_grouper_60_cmsy_free$ref_pts
gulf_grouper_60_cmsy_free$ref_ts

##results: viable r-k pairs graph is super weird; MSY= 22.204; BMSY < 0.8 = overfished except for 2014 and 2015 which is barely over. 2013 is exactly 8

```
















