---
title: "CMSY_Octopus_Free"
author: "Juliette"
date: "October 31, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages 

```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(sf)
  library(rfishbase)
  library(plotly)
  library(fishmethods)
  library(devtools)
devtools::install_github("cfree14/datalimited2") 
  library(datalimited2) # Chris Free updated package for CMSY2
})


```


#Load catch data of species
#Loading datset of 7 species with catch data and catch inflated to 20%, 40% and 60% unreported catch 

MT - regular yearly catch 
MT_20 - inflated to 20% unreported catch
MT_40- inflated to 40% unreported catch
MT_60 - inflated to 60% unreported catch
```{r}
#loading catch data of 6 species with more than 5 years of catch data, detailed code for this dataset is in the "landing sites.rmd" in docs 
focalspeciescatch<-read.csv(here("docs", "focalspeciescatch.csv"))

unique(focalspeciescatch$NombreCientifico) #6 species 

#create a new dataframe to isolate your species of interest 
octopus_sp<-focalspeciescatch%>%
  filter(NombreCientifico=="Octopus sp")

#Create vectors for the cmsy2 function
year_octopus_sp <- c(octopus_sp$Ano) #vector of years
catch_octopus_sp <- c(octopus_sp$MT) #vector of catch date 

#new datafram to isolate catch increase by 20%
catch20_octopus_sp<- c(octopus_sp$MT_20)
#new datafram to isolate catch increase by 40%
catch40_octopus_sp<- c(octopus_sp$MT_40)
#new datafram to isolate catch increase by 60%
catch60_octopus_sp<- c(octopus_sp$MT_60)



```


```{r}
#Plots catch over given years, simply change the name of the dataframe ie "Octopus"
graph_octopus <-ggplot(octopus_sp, aes(x=Ano, y=MT))+
  geom_line(size=1)+
  ggtitle("Octopus Species Catch")+
  geom_point()+
  geom_line()+
  labs(x="Year", y="Yearly total catch catch (MT)")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

ggplotly(graph_octopus)


```



FAO considers a maximally sustainable fished stock to be between 0.8 and 1.2 BMSY, an overfished stock to be <0.8 BMSY, and an underfished stock to be >1.2 BMSY. For US federally managed fisheries, NOAA reports on what fraction of stocks are overfished (https://www.fisheries.noaa.gov/feature-story/status-stocks-2017), usually defined as being <0.5 BMSY, though the exact ratio differs by region and type of stock

Paper: https://academic.oup.com/icesjms/advance-article/doi/10.1093/icesjms/fsy138/5133277

```{r}

?cmsy2

#Regular landings 
octopus_sp_cmsy_free <- cmsy2(year=year_octopus_sp, catch=catch_octopus_sp, resilience = "Medium")

octopus_sp_cmsy_free_plots <- plot_dlm(octopus_sp_cmsy_free)

octopus_sp_cmsy_free
octopus_sp_cmsy_free_plots
octopus_sp_cmsy_free$ref_pts
octopus_sp_cmsy_free$ref_ts

##results:MSY= 171.454; Bmsy = 0.604; B/Bmsy in last year  = 0.93


#Landings inflated 20%
octopus_sp_20_cmsy_free <- cmsy2(year=year_octopus_sp, catch=catch20_octopus_sp, resilience = "Medium")

octopus_sp_20_cmsy_free_plots <- plot_dlm(octopus_sp_20_cmsy_free)

octopus_sp_20_cmsy_free$ref_pts
octopus_sp_20_cmsy_free$ref_ts

##results:MSY= 204.294;  Bmsy = 0.716; B/Bmsy in last year  = 0.929


#Landings inflated 40%
octopus_sp_40_cmsy_free <- cmsy2(year=year_octopus_sp, catch=catch40_octopus_sp, resilience = "Medium")

octopus_sp_40_cmsy_free_plots <- plot_dlm(octopus_sp_40_cmsy_free)

octopus_sp_40_cmsy_free$ref_pts
octopus_sp_40_cmsy_free$ref_ts

##results: MSY= 237.990; Bmsy = 0.847; B/Bmsy in last year  = 0.936


#Landings inflated 60%
octopus_sp_60_cmsy_free <- cmsy2(year=year_octopus_sp, catch=catch60_octopus_sp, resilience = "Medium")

octopus_sp_60_cmsy_free_plots <- plot_dlm(octopus_sp_60_cmsy_free)

octopus_sp_60_cmsy_free$ref_pts
octopus_sp_60_cmsy_free$ref_ts

##results: MSY= 273.372	; Bmsy = 0.977; B/Bmsy in last year  = 0.969

```












