---
title: "yellow_snapper_cmsy_free"
author: "Vienna Saccomanno"
date: "November 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages}

suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(sf)
  library(rfishbase)
  #library(plotly)
  library(fishmethods)
  library(devtools)
devtools::install_github("cfree14/datalimited2") 
  library(datalimited2) # Chris Free updated package for CMSY2
})

```

#Load catch data of species
#Loading datset of 7 species with catch data and catch inflated to 20%, 40% and 60% unreported catch 

MT - regular yearly catch 
MT_20 - inflated to 20% unreported catch
MT_40- inflated to 40% unreported catch
MT_60 - inflated to 60% unreported catch

```{r}
#loading catch data of 6 species with more than 5 years of catch data, detailed code for this dataset is in the "landing sites.rmd" in docs 
focalspeciescatch<-read.csv(here("docs", "focalspeciescatch.csv"))
#View(focalspeciescatch)

unique(focalspeciescatch$NombreCientifico) #7 species 

#create a new dataframe to isolate your species of interest 
snapper_sp<-focalspeciescatch%>%
  filter(NombreCientifico=="Lutjanus argentiventris")
#View(snapper_sp)

#Create vectors for the cmsy2 function
year_snapper_sp <- c(snapper_sp$Ano) #vector of years
catch_snapper_sp <- c(snapper_sp$MT) #vector of catch date 
#View(catch_snapper_sp)

#new datafram to isolate catch increase by 20%
catch20_snapper_sp<- c(snapper_sp$MT_20)
#new datafram to isolate catch increase by 40%
catch40_snapper_sp<- c(snapper_sp$MT_40)
#new datafram to isolate catch increase by 60%
catch60_snapper_sp<- c(snapper_sp$MT_60)

```

```{r plots}

#Plots catch over given years
graph_snapper <-ggplot(snapper_sp, aes(x=Ano, y=MT))+
  geom_line(size=1)+
  ggtitle("Snapper Catch")+
  geom_point()+
  geom_line()+
  labs(x="Year", y="Yearly total catch catch (MT)")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

ggplotly(graph_snapper)
```
FAO considers a maximally sustainable fished stock to be between 0.8 and 1.2 BMSY, an overfished stock to be <0.8 BMSY, and an underfished stock to be >1.2 BMSY. For US federally managed fisheries, NOAA reports on what fraction of stocks are overfished (https://www.fisheries.noaa.gov/feature-story/status-stocks-2017), usually defined as being <0.5 BMSY, though the exact ratio differs by region and type of stock

Paper: https://academic.oup.com/icesjms/advance-article/doi/10.1093/icesjms/fsy138/5133277


```{r}


#Regular landings 
snapper_sp_cmsy_free <- cmsy2(year=year_snapper_sp, catch=catch_snapper_sp, resilience = "Low")

snapper_sp_cmsy_free_plots <- plot_dlm(snapper_sp_cmsy_free)


snapper_sp_cmsy_free_plots
snapper_sp_cmsy_free$ref_pts
snapper_sp_cmsy_free$ref_ts

##results:MSY= 0.000338; Bmsy = 0.0024; B/Bmsy in last year  = 0.23; Fishing mortality in last year = 0.101; Exploitation F/Fmsy  = 1.55


#Landings inflated 20%
snapper_sp_20_cmsy_free <- cmsy2(year=year_snapper_sp, catch=catch20_snapper_sp, resilience = "Low")

snapper_sp_20_cmsy_free_plots <- plot_dlm(snapper_sp_20_cmsy_free)

snapper_sp_20_cmsy_free$ref_pts
snapper_sp_20_cmsy_free$ref_ts
##results 20%:MSY= 0.00041;  Bmsy = 0.0029; B/Bmsy in last year  = 0.234; Fishing mortality in last year = 0.098; Exploitation F/Fmsy  = 1.48


#Landings inflated 40%
snapper_sp_40_cmsy_free <- cmsy2(year=year_snapper_sp, catch=catch40_snapper_sp, resilience = "Low")

snapper_sp_40_cmsy_free_plots <- plot_dlm(snapper_sp_40_cmsy_free)

snapper_sp_40_cmsy_free$ref_pts
snapper_sp_40_cmsy_free$ref_ts

##results 40%: MSY= 0.000485; Bmsy = 0.00344; B/Bmsy in last year  = 0.229; Fishing mortality in last year = 0.0985; Exploitation F/Fmsy  = 1.52


#Landings inflated 60%
snapper_sp_60_cmsy_free <- cmsy2(year=year_snapper_sp, catch=catch60_snapper_sp, resilience = "Medium")

snapper_sp_60_cmsy_free_plots <- plot_dlm(snapper_sp_60_cmsy_free)

snapper_sp_60_cmsy_free$ref_pts
snapper_sp_60_cmsy_free$ref_ts

##results 60%: MSY= 0.000651; Bmsy = 0.0023; B/Bmsy in last year  =  0.22; Fishing mortality in last year = 0.175; Exploitation F/Fmsy  = 1.4


```

