---
title: "MSY_humphead_parrot"
author: "Juliette Verstaen"
date: "10/27/2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Packages 

```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(sf)
  library(rfishbase)
  library(plotly)
  library(fishmethods)
  library(devtools)
install_github("James-Thorson/FishLife")
library(FishLife)
})


```


#Load catch data of species

```{r}
#loading catch data of 6 species with more than 5 years of catch data, detailed code for this dataset is in the "landing sites.rmd" in docs 
focalspeciescatch<-read.csv(here("docs", "focalspeciescatch.csv"))

unique(focalspeciescatch$NombreCientifico) #6 species 

#create a new dataframe to isolate your species of interest 
bumphead_parrot<-focalspeciescatch%>%
  filter(NombreCientifico=="Scarus perrico")

```



```{r}
#Plots catch over given years, simply change the name of the dataframe ie "Octopus"
graph_BumpheadParrot <-ggplot(bumphead_parrot, aes(x=Ano, y=MT))+
  geom_line(size=1)+
  ggtitle("Bumphead Parrot")+
  geom_point()+
  geom_line()+
  labs(x="Year", y="Yearly total catch catch (MT)")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

ggplotly(graph)


```


#Run CatchMSY
https://onlinelibrary.wiley.com/doi/abs/10.1111/j.1467-2979.2012.00485.x

Above is the link to the reference publication "A simple method for estimating MSY from catch and resilience"

```{r}
year_humphead_parrot<-c(humphead_parrot$Ano) #vector of years
catch_humphead_parrot<-c(humphead_parrot$MT) #vector of catch date 

?catchmsy #Provides more information on the function itself

#Initial catch divided by highest catch; use ranges listed in the Martell publication based on this ratio
0.1584/0.1584

#final year catch divided by highest catch; use ranges listed in the Martell publication based on this ratio
0.1395/0.1584


catchmsy(year=year_humphead_parrot,
                catch=catch_humphead_parrot,
    l0=list(low=0.3,up=0.6,step=0),#biomass in year in relation to K, Initial catch divided by highest catch
    lt=list(low= 0.3,up=0.7,refyr=2015),#biomass in last year in relation to K, years catch divided by highest catch
    k=list(dist="unif",low=0.1584,up=15.84), #carrying capacity; low=highest reported catch, high=highest catch*100
    r=list(dist="unif",low=0.3,up=.9), #intrinsic growth rate based on resiliene 
    M=list(dist="unif",low=0.1,up=0.9), #Natural mortality 
    nsims=30000, #Monte carlo simulations 
    catchout = (1), #saving the monte carlo simulations that can later be graphed
    grout = 1, #output just to console, 
    graphs = c(1, 2,3,4,5,6,7,8,9,10,11))


#on fish base "Resilience (Ref. 69278):  Medium, minimum population doubling time 1.4 - 4.4 years (Preliminary K or Fecundity.)"

```

Graphs:
1. Time series of catched with overlaid estimate of MSY (solid line) and and 95% limit (dashed lines)
2. Point plot of plausible k versus r values, dots show r-k combinations that are compatible with catch series
3. Histogram of plausible r values, posterior densities distribution
4. Histogram of plausible k values, posterior densities distribution
5. Histogram of M values, posterior densities distribution
6. Histogram of MSY from plausible values of l0,k,r, and Bmsy/k 
7. Histogram of Bmsy from plausible values of l0,k,r, and Bmsy/k
8. Histogram of Fmsy from plausible values of l0,k,r, and Bmsy/k; fishing mortality at MSY is r/2
9. Histogram of Umsy values from Fmsy and M; Umsy is exploitation rate at MSY
10. Histogram of overfishing limit (OFL) in last year+1 values from Umsys
11. Line plots of accepted and rejected biomass trajectores with median and 2.5th and 97.5th percentiles (in red)
