---
title: "report_figures_juliette"
author: "Juliette Verstaen"
date: "2/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE, message=FALSE}
library(ggplot2)
library(here)
library(plotly)
library(tidyverse)
library(gganimate)
library(ggrepel)
library(ggridges)
library(ggpubr)
library(gridExtra)
library(grid)
```

#importing the dataset only looking at 2015-2065
```{r}
res<-read.csv(here::here("Scenarios", "PatchModel_size.csv"))%>%
  filter(Year <= 2065 & Adjusted== "MT")
bmsy<- expression(paste(B/B[MSY]))
fmsy <- expression(paste(F/F[MSY]))

```

Summing up cummulative biomass and pv of all genuses OA
```{r}

circle<- res%>%
  filter(Total_Area == "5%" | Total_Area== "BAU") %>%
  group_by(Status, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
  mutate(Biomass_est=Biomass_est/1000)%>%
  mutate(PV_est=PV_est/1000000)
circle$Status<- as.factor(circle$Status)

#bio_pv_2035 <- res%>%
#  filter(Total_Area == "5%")%>%
#  filter(Year <= "2035")%>%
#  group_by(Status, Adjusted)%>%
#  summarize(Biomass_est=sum(Biomass_est), 
#            Catch_est=sum(Catch_est), 
#            PV_est=sum(PV_est))
#bio_pv_2035$Status<- as.factor(bio_pv_2035$Status)


```


```{r}

circle_graph <- ggplot(circle) +
  geom_point(aes(x= Biomass_est, y= PV_est,size=Catch_est, color = Status), shape = 21)+
  guides(size= "none")+
  scale_size_continuous(range = c(15, 30)) +
  annotate(geom="text", x=1256.866, y=361.405921, label="318K MT",
              color="black") +
  annotate(geom="text", x=1253.392, y=364.691491, label="319K MT",
              color="black")+
  annotate(geom="text", x=1247.927, y=369.812271, label="321K MT",
              color="black")+
  annotate(geom="text", x=1240.207, y=375.365648, label="324K MT",
              color="black")+
  annotate(geom="text", x=1188.948, y=377.850277, label="332K MT",
              color="black")+
  xlim(1170, 1270)+
  ylim(360, 380)+
  theme_classic()+
  xlab("Biomass (1000 MT)") +
  ylab("Profits (Millions US$)")
  

circle_graph

#ggsave("agg_circles.jpg", width=7, height=5, dpi=300)

```

Summing up cummulative biomass and pv of all genuses F= FMSY
Every column ends up being the same regardless of implementation date

side notw for seleni: looked at data, BAU (status=0) only for the 5% implementation option; would be super useful to compare graphs if it was for all reserve sizes
```{r}


fmsy<- read.csv(here::here("Scenarios", "PatchModel_FMSY.csv"))%>%
  filter(Adjusted=="MT")


circle_fmsy<- fmsy%>%
  filter(Total_Area == "5%") %>%
  group_by(Status, Adjusted) %>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))

circle_fmsy$Status<- as.factor(circle_fmsy$Status)


```

Circle graphs with 40% protected

```{r}

circle_40<- res%>%
  filter(Total_Area == "40%") %>%
  group_by(Status, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
circle_40$Status<- as.factor(circle_40$Status)


circle_40_graph <- ggplot(circle_40) +
  geom_point(aes(x= Biomass_est, y= PV_est, size=Catch_est, color = Status), shape = 21)+
  scale_size_continuous(range = c(11, 25)) +
  theme_classic()+
  ggtitle("Aggregate Regional Affects 40% Protected")
  

circle_40_graph

#ggsave("agg_circles_40.jpg", width=7, height=5, dpi=300)

```


Circle graphs with 30% protected

```{r}

circle_30<- res%>%
  filter(Total_Area == "30%") %>%
  group_by(Status, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
circle_30$Status<- as.factor(circle_30$Status)


circle_30_graph <- ggplot(circle_30) +
  geom_point(aes(x= Biomass_est, y= PV_est, size=Catch_est, color = Status), shape = 21)+
  scale_size_continuous(range = c(11, 25)) +
  theme_classic()+
  ggtitle("Aggregate Regional Affects 30% Protected")
  

circle_30_graph

#ggsave("agg_circles_30.jpg", width=7, height=5, dpi=300)

```



Graphs seperated out by implmentation date (too similar to do all on one graph)
y axis= year; y-axis = biomass; size= catch, color = money made
OA
**These are interesting because you can see the delayed effect of fishing pressure (with catch and increase profits) after the biomass spike and how the fishing pressure contines to be the same even though biomass decreases and then they bascially crash the fishery

```{r}

library(dplyr)

linepoint <- res %>%
    filter(Total_Area == "5%" | Total_Area == "BAU") %>%
  group_by(Year, Status, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est)) %>%
  mutate(Biomass_est=Biomass_est/1000)
linepoint$Status<- as.factor(linepoint$Status)
  

#Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "MT") %>%
  filter(year>="2005") %>%
  filter(year != "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b))%>%
  mutate(b=b/1000)

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint %>%
  filter(Status== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint, Status == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint, Status == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint, Status == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint, Status == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("BAU")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("2015")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("2020")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("2025")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est, show.legend= FALSE))+
  geom_point()+
  ggtitle("2030")+
  ylab("Biomass 1000 (MT)")+
  theme_classic()

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend=FALSE)
all
ggsave("biomass_time.jpg", width=10, height=12, dpi=300)
```



Graphs seperated out by implmentation date (too similar to do all on one graph)
y axis= year; y-axis = biomass; size= catch, color = money made
F=Fmsy
** can see where the biomass equilibrium happenes

```{r}

library(dplyr)

fmsy<- read.csv(here::here("Scenarios", "PatchModel_FMSY.csv"))%>%
  filter(Adjusted=="MT")


linepoint_fmsy<- fmsy%>%
  filter(Total_Area == "5%") %>%
  group_by(Year, Status, Adjusted) %>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))

linepoint_fmsy$Status<- as.factor(circle_fmsy$Status)

Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "MT") %>%
  filter(year>="2005") %>%
  filter(year != "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b))

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint_fmsy %>%
  filter(Status== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint_fmsy, Status == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint_fmsy, Status == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint_fmsy, Status == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint_fmsy, Status == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("BAU")

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2015")

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2020")

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2025")

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2030")

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend="bottom")
all
#ggsave("biomass_time_fmsy.jpg", width=10, height=12, dpi=300)
```

Graphs seperated out by implmentation date (too similar to do all on one graph)
y axis= year; y-axis = biomass; size= catch, color = money made
OA and 40% protected


```{r}

library(dplyr)

linepoint <- res %>%
    filter(Total_Area == "40%") %>%
  group_by(Year, Status, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
linepoint$Status<- as.factor(linepoint$Status)
  

Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "MT") %>%
  filter(year>="2005") %>%
  filter(year != "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b))

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint %>%
  filter(Status== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint, Status == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint, Status == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint, Status == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint, Status == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("BAU")

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2015")

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2020")

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2025")

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2030")

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend="bottom")
all
#ggsave("biomass_time_40protect.jpg", width=10, height=12, dpi=300)
```

Protect 30
```{r}

library(dplyr)

linepoint <- res %>%
    filter(Total_Area == "30%") %>%
  group_by(Year, Status, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
linepoint$Status<- as.factor(linepoint$Status)
  

Genus_ts <- read_csv("data/Genus_ts.csv")

historic <- Genus_ts %>%
  filter(Adjusted == "MT") %>%
  filter(year>="2005") %>%
  filter(year != "2015") %>%
  group_by(year) %>%
  summarize(catch=sum(catch),
            b=sum(b))

colnames(historic) <- c("Year", "Catch_est", "Biomass_est")

initial <-linepoint %>%
  filter(Status== "0") 
initial <- full_join(historic, initial, by=c("Year", "Biomass_est", "Catch_est"))

second <- filter(linepoint, Status == "2015")
second <- full_join(historic, second, by=c("Year", "Biomass_est", "Catch_est"))

third <- filter(linepoint, Status == "2020")
third <- full_join(historic, third, by=c("Year", "Biomass_est", "Catch_est"))

fourth <- filter(linepoint, Status == "2025")
fourth <- full_join(historic, fourth, by=c("Year", "Biomass_est", "Catch_est"))

fifth <- filter(linepoint, Status == "2030")
fifth <- full_join(historic, fifth, by=c("Year", "Biomass_est", "Catch_est"))

initial_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("BAU")

second_graph <- ggplot(second,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2015")

third_graph <- ggplot(third,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2020")

fourth_graph <- ggplot(fourth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2025")

fifth_graph <- ggplot(fifth,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  ggtitle("Implement 2030")

all<-ggarrange(initial_graph, second_graph, third_graph, fourth_graph, fifth_graph, nrow=3, ncol=2, common.legend = TRUE, legend="bottom")
all
#ggsave("biomass_time_30protect.jpg", width=10, height=12, dpi=300)
```







Juliette Notebook:
```{r}

linepoint <- res %>%
    filter(Total_Area == "5%") %>%
  group_by(Year, Status, Adjusted)%>%
  summarize(Biomass_est=sum(Biomass_est), 
            Catch_est=sum(Catch_est), 
            PV_est=sum(PV_est))
linepoint$Status<- as.factor(linepoint$Status)
  
initial <-filter(linepoint, Status== "0")
second <- filter(linepoint, Status == "2015")
third <- filter(linepoint, Status == "2020")
fourth <- filter(linepoint, Status == "2025")
fifth <- filter(linepoint, Status == "2030")

linepoint_graph <- ggplot(initial,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point()+
  geom_point(data= second, aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point(data = third, aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point(data = fourth, aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point(data = fifth, aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))
  
linepoint_graph    
  
linepoint_graph_2 <- ggplot(linepoint,aes(x= Year, y = Biomass_est, colour = PV_est, size= Catch_est))+
  geom_point(data=linepoint[linepoint$Status =="0", ])+
  geom_point(data=linepoint[linepoint$Status =="2015", ])+
  geom_point(data=linepoint[linepoint$Status =="2020", ])+
  geom_point(data=linepoint[linepoint$Status =="2025", ])+
  geom_point(data=linepoint[linepoint$Status =="2030", ])

linepoint_graph_2



  
 
```
