---
title: "Graph MPA patch model output"
author: "Seleni Cruz"
date: "January 7, 2019"
output:
  html_document: default
  papersize: legal
  pdf_document: default
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE}
suppressPackageStartupMessages({
library(dplyr)
library(here)
library(ggplot2)
library(plotly)
})
```


#Genera Biomass projection when catch data was not inflated

```{r, echo=FALSE,  message=FALSE}
Biomass<-read.csv(here::here("data", "Genus_ts.csv"))%>%
  filter(Adjusted=="MT")


catch<- readRDS(here::here("data", "Species_ts.rds"))

Genus<-read.csv(here::here("data", "Genus_patchmodel.csv"))%>%
  filter(Adjusted=="MT")

graph1<-ggplot(Genus, aes(x=Year, y=Biomass_est, color=Status))+
 geom_line(size=1)+
  #geom_point()+
  labs(x="Year", y="Biomass (MT)", title="Biomass by Genera 2015-2035")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

graph2<-graph1+
   facet_wrap(~ Name, scales = "free_y", ncol=2)

```

```{r, fig.height= 30, fig.width=20, echo=FALSE}
graph2
```

#Genera Biomass projection when catch data was inflated 20%
```{r, echo=FALSE,  message=FALSE, }
Genus<-read.csv(here::here("data", "Genus_patchmodel.csv"))%>%
  filter(Adjusted=="MT_20")

graph1<-ggplot(Genus, aes(x=Year, y=Biomass_est, color=Status))+
 geom_line(size=1)+
  #geom_point()+
  labs(x="Year", y="Biomass (MT)", title="Biomass by Genera 2015-2035")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

graph2<-graph1+
   facet_wrap(~ Name, scales = "free_y", ncol=2)

```

```{r, fig.height= 30, fig.width=20, , echo=FALSE}
graph2
```

#Genera Biomass projection when catch data was inflated 40%

```{r, echo=FALSE,  message=FALSE }
Genus<-read.csv(here::here("data", "Genus_patchmodel.csv"))%>%
  filter(Adjusted=="MT_40")

graph1<-ggplot(Genus, aes(x=Year, y=Biomass_est, color=Status))+
 geom_line(size=1)+
  #geom_point()+
  labs(x="Year", y="Biomass (MT)", title="Biomass by Genera 2015-2035")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

graph2<-graph1+
   facet_wrap(~ Name, scales = "free_y", ncol=2)

```

```{r, fig.height= 30, fig.width=20, echo=FALSE}
graph2
```

#Genera Biomass projection when catch data was inflated 60%

```{r, echo=FALSE,  message=FALSE }
Genus<-read.csv(here::here("data", "Genus_patchmodel.csv"))%>%
  filter(Adjusted=="MT_60")

graph1<-ggplot(Genus, aes(x=Year, y=Biomass_est, color=Status))+
 geom_line(size=1)+
  #geom_point()+
  labs(x="Year", y="Biomass (MT)", title="Biomass by Genera 2015-2035")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

graph2<-graph1+
   facet_wrap(~ Name, scales = "free_y", ncol=2)

```

```{r, fig.height= 30, fig.width=20, echo=FALSE}
graph2
```

#Species Biomass projection when catch data was not inflated

```{r, echo=FALSE,  message=FALSE }
Species<-read.csv(here::here("data", "Species_patchmodel.csv"))%>%
  filter(Adjusted=="MT")

graph1<-ggplot(Species, aes(x=Year, y=Biomass_est, color=Status))+
 geom_line(size=1)+
  #geom_point()+
  labs(x="Year", y="Biomass (MT)", title="Biomass by Species 2015-2035")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

graph2<-graph1+
   facet_wrap(~ Name, scales = "free_y", ncol=2)

```

```{r, fig.height= 10, fig.width=10, echo=FALSE}
graph2
```

#Species Biomass projection when catch data was inflated 20%

```{r, echo=FALSE,  message=FALSE }
Species<-read.csv(here::here("data", "Species_patchmodel.csv"))%>%
  filter(Adjusted=="MT_20")

graph1<-ggplot(Species, aes(x=Year, y=Biomass_est, color=Status))+
 geom_line(size=1)+
  #geom_point()+
  labs(x="Year", y="Biomass (MT)", title="Biomass by Species 2015-2035")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

graph2<-graph1+
   facet_wrap(~ Name, scales = "free_y", ncol=2)

```

```{r, fig.height= 10, fig.width=10, echo=FALSE}
graph2
```

#Species Biomass projection when catch data was inflated 40%

```{r, echo=FALSE,  message=FALSE }
Species<-read.csv(here::here("data", "Species_patchmodel.csv"))%>%
  filter(Adjusted=="MT_40")

graph1<-ggplot(Species, aes(x=Year, y=Biomass_est, color=Status))+
 geom_line(size=1)+
  #geom_point()+
  labs(x="Year", y="Biomass (MT)", title="Biomass by Species 2015-2035")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

graph2<-graph1+
   facet_wrap(~ Name, scales = "free_y", ncol=2)

```

```{r, fig.height= 10, fig.width=10, echo=FALSE}
graph2
```

#Species Biomass projection when catch data was inflated 60%

```{r, echo=FALSE,  message=FALSE }
Species<-read.csv(here::here("data", "Species_patchmodel.csv"))%>%
  filter(Adjusted=="MT_60")

graph1<-ggplot(Species, aes(x=Year, y=Biomass_est, color=Status))+
 geom_line(size=1)+
  #geom_point()+
  labs(x="Year", y="Biomass (MT)", title="Biomass by Species 2015-2035")+
  theme_classic()+
  scale_x_continuous(expand=c(0,0))+
  scale_y_continuous(expand=c(0,0))+
  theme(legend.title=element_blank())

graph2<-graph1+
   facet_wrap(~ Name, scales = "free_y", ncol=2)

```

```{r, fig.height= 10, fig.width=10, echo=FALSE}
graph2
```




